### 2014-08-18 Docs/flowchart/flowchart.tex
some latex tweaks

The compressible momentum equation (written in terms of velocity is):
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla p = -\rho |g| \er
\end{equation}
Subtracting off the base state, and defining the perturbational
pressure (sometimes called the dynamic pressure) as $\pi = p - p_0$,
and perturbational density as $\rho' = \rho - \rho_0$, we have:
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla \pi = -\rho' |g| \er
\end{equation}
or
\begin{equation}
\frac{\partial \Ub}{\partial t} + \Ub \cdot \nabla \Ub + \frac{1}{\rho} \nabla \pi =
   -\frac{\rho^\prime}{\rho} |g| \er
\end{equation}
This is the form of the momentum equation that we solved in papers
I--IV and in the multilevel paper.

@@

We decompose the full velocity field into a base state velocity,
$w_0$, that governs the base state dynamics, and a local velocity,
$\Ubt$, that governs the local dynamics, i.e., 
\begin{equation}
\Ub = w_0(r,t)\eb_r + \Ubt(\xb,t).
\end{equation}
with
$\overline{(\Ubt\cdot\eb_r)} = 0$ and
$w_0 = \overline{(\Ub\cdot\eb_r)}$---the motivation for this splitting was given in paper~II.
The velocity evolution equations are then 
\begin{eqnarray}
\frac{\partial w_0}{\partial t} &=& -w_0\frac{\partial w_0}{\partial
  r} - \frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r},\label{eq:w0
  evolution}\\ 
%
\frac{\partial\Ubt}{\partial t} &=& -(\Ubt + w_0\er)\cdot\nabla\Ubt
  - \left(\Ubt\cdot\eb_r\right)\frac{\partial w_0}{\partial r}\eb_r -
\frac{\beta_0}{\rho}\nabla\left(\frac{\pi}{\beta_0} \right) +
\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\eb_r -
\frac{\rho-\rho_0}{\rho}g\eb_r.\label{eq:flow:utildeupd}
\end{eqnarray}
where $\pi_0$ is the base state component of the perturbational pressure.
By laterally averaging to equation (\ref{eq:U divergence}),
we obtain a divergence constraint for $w_0$:
\begin{equation}
\nabla\cdot(\beta_0 w_0 \eb_r) = 
    \beta_0\left(\Sbar - \frac{1}{\gammabar p_0}
           \frac{\partial p_0}{\partial t}\right).\label{eq:w0 divergence}
\end{equation}
The divergence constraint for $\Ubt$ can be found by subtracting
(\ref{eq:w0 divergence}) into (\ref{eq:U divergence}), resulting in
\begin{equation}
\nabla\cdot\left(\beta_0\Ubt\right) = \beta_0\left(S-\Sbar\right).\label{eq:utilde divergence}
\end{equation}

@@

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then have \MarginPar{I think that we include to $\delta \Gamma_1^2$ now}
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 = S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ub \cdotb \nablab p_0 \enskip , \label{eq:gammafull}
\end{equation}
The base state evolution equation is the average of this over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
where we see that the $[\delta \Gamma_1/(\Gamma_1^2 p_0)] \partial p_0/\partial t$ terms averages to zero, since the average of $\delta\Gamma_1$ term is zero.
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}

>>>>

The compressible momentum equation (written in terms of velocity is):
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla p = -\rho |g| \er
\end{equation}
Subtracting off the base state, and defining the perturbational
pressure (sometimes called the dynamic pressure) as $\pi \equiv p - p_0$,
and perturbational density as $\rho' \equiv \rho - \rho_0$, we have:
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla \pi = -\rho' |g| \er
\end{equation}
or
\begin{equation}
\frac{\partial \Ub}{\partial t} + \Ub \cdot \nabla \Ub + \frac{1}{\rho} \nabla \pi =
   -\frac{\rho^\prime}{\rho} |g| \er
\end{equation}
This is the form of the momentum equation that we solved in papers
I--IV and in the multilevel paper.

@@

We decompose the full velocity field into a base state velocity,
$w_0$, that governs the base state dynamics, and a local velocity,
$\Ubt$, that governs the local dynamics, i.e., 
\begin{equation}
\Ub = w_0(r,t)\eb_r + \Ubt(\xb,t).
\end{equation}
with
$\overline{(\Ubt\cdot\eb_r)} = 0$ and
$w_0 = \overline{(\Ub\cdot\eb_r)}$---the motivation for this splitting was given in paper~II.
The velocity evolution equations are then 
\begin{align}
\frac{\partial w_0}{\partial t} &= -w_0\frac{\partial w_0}{\partial
  r} - \frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r},\label{eq:w0
  evolution}\\ 
%
\frac{\partial\Ubt}{\partial t} &= -(\Ubt + w_0\er)\cdot\nabla\Ubt
  - \left(\Ubt\cdot\eb_r\right)\frac{\partial w_0}{\partial r}\eb_r -
\frac{\beta_0}{\rho}\nabla\left(\frac{\pi}{\beta_0} \right) +
\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\eb_r -
\frac{\rho-\rho_0}{\rho}g\eb_r.\label{eq:flow:utildeupd}
\end{align}
where $\pi_0$ is the base state component of the perturbational pressure.
By laterally averaging to equation (\ref{eq:U divergence}),
we obtain a divergence constraint for $w_0$:
\begin{equation}
\nabla\cdot(\beta_0 w_0 \eb_r) = 
    \beta_0\left(\Sbar - \frac{1}{\gammabar p_0}
           \frac{\partial p_0}{\partial t}\right).\label{eq:w0 divergence}
\end{equation}
The divergence constraint for $\Ubt$ can be found by subtracting
(\ref{eq:w0 divergence}) into (\ref{eq:U divergence}), resulting in
\begin{equation}
\nabla\cdot\left(\beta_0\Ubt\right) = \beta_0\left(S-\Sbar\right).\label{eq:utilde divergence}
\end{equation}

@@

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then
have 
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 
 \left [ 1 - \frac{\delta\Gamma_1}{\gammabar} + \frac{(\delta\Gamma_1)^2}{\gammabar^2} \right ]
= S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} 
 \left [ 1 - \frac{\delta\Gamma_1}{\gammabar} + \frac{(\delta\Gamma_1)^2}{\gammabar^2} \right ] \\
\end{equation}
Grouping by order of the correction, we have
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 
= S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\underbrace{\frac{\delta \Gamma_1}{\gammabar^2 p_0} 
            \left [\frac{\partial p_0}{\partial t} + \Ub \cdotb \nablab p_0\right ]}_{\mbox{first order corrections}} 
 -
  \underbrace{\frac{(\delta\Gamma_1)^2}{\gammabar^3 p_0}
            \left [ \frac{\partial p_0}{\partial t} + \Ub \cdotb \nablab p_0 \right ]}_{\mbox{second order corrections}} \enskip , \label{eq:gammafull}
\end{equation}

\subsubsection{Keeping to First Order in $\delta\Gamma_1$}
The base state evolution equation is the average of Eq.~\ref{eq:gammafull} over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
where we see that the $[\delta \Gamma_1/(\Gamma_1^2 p_0)] \partial p_0/\partial t$ terms averages to zero, since the average of $\delta\Gamma_1$ term is zero.
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}
